---
title: "AS3-1: 數位偵探"
author: "第 15 組"
date: "`r Sys.time()`"
output: 
  html_document:
    highlight: pygments
    theme: flatly
    css: style.css
---

組員：`B044030015 許效軒`  `B046060036 王文弘`  `B054012011 黃冠綾`  `B046060027 姚詠馨`  `B046060035 張文瑜`  `M074020024 楊長舜`

```{r results='hide', message=FALSE, warning=FALSE, echo=F}
# 這些程式碼設定網頁的格式，並安裝、載入一些基本的套件，請大家不要去改動<br>
rm(list=ls(all=T))
knitr::opts_chunk$set(comment = NA)
knitr::opts_knit$set(global.par = TRUE)
par(cex=0.8)
options(scipen=20, digits=4, width=90)
#
if(!require(pacman)) install.packages("pacman")
pacman::p_load(dplyr, d3heatmap)
```
<hr>

犯罪是一個國際關注的問題，但它在不同的國家以不同的方式記錄和處理。 在美國，聯邦調查局（FBI）記錄了暴力犯罪和財產犯罪。 此外，每個城市都記錄了犯罪行為，一些城市發布了有關犯罪率的數據。 伊利諾伊州芝加哥市從2001年開始在線發布犯罪數據。

芝加哥是美國人口第三多的城市，人口超過270萬。在這個作業裡面，我們將關注一種特定類型的財產犯罪，稱為「汽車盜竊」，我們將使用R中的一些基本數據分析來了解芝加哥的汽車盜竊紀錄。請載入文件"data/mvtWeek1.csv"：以下是各欄位的描述：

+ `ID`: a unique identifier for each observation
+ `Date`: the date the crime occurred
+ `LocationDescription`: the location where the crime occurred
+ `Arrest`: whether or not an arrest was made for the crime (TRUE if an arrest was made, and FALSE if an arrest was not made)
+ `Domestic`: whether or not the crime was a domestic crime, meaning that it was committed against a family member (TRUE if it was domestic, and FALSE if it was not domestic)
+ `Beat`: the area, or "beat" in which the crime occurred. This is the smallest regional division defined by the Chicago police department.
+ `District`: the police district in which the crime occured. Each district is composed of many beats, and are defined by the Chicago Police Department.
+ `CommunityArea`: the community area in which the crime occurred. Since the 1920s, Chicago has been divided into what are called "community areas", of which there are now 77. The community areas were devised in an attempt to create socially homogeneous regions.
+ `Year`: the year in which the crime occurred.
+ `Latitude`: the latitude of the location at which the crime occurred.
+ `Longitude`: the longitude of the location at which the crime occurred.

<br>

- - -

###  Section-1 Loading the Data

【1.1】How many rows of data (observations) are in this dataset?
```{r}
#191641
data = read.csv("data/mvtWeek1.csv") #讀入資料並命名資料框為data
nrow(data)#從列數數量了解觀察值數量
```

檢查各欄位的資料格式
```{r}
#使用str()可了解個欄位的格式(如factor,logistic,integer,number)
str(data)
head(data)
```

類別(Factor) versus 字串(Character)

【1.2】How many variables are in this dataset?
```{r}
#11
ncol(data) #從欄位數量可了解有多少個變數
```


【1.3】Using the "max" function, what is the maximum value of the variable "ID"?
```{r}
#9181151
max(data$ID) #max()可了解最大值
```


【1.4】 What is the minimum value of the variable "Beat"?
```{r}
#111
min(data$Beat) #min()可了解最小值
```


【1.5】 How many observations have value TRUE in the Arrest variable (this is the number of crimes for which an arrest was made)?
```{r}
#15536
sum(data$Arrest == TRUE) #用sum()取得案件有被抓(data$arrest為true)的觀察值數量
```

【1.6】 How many observations have a LocationDescription value of ALLEY?
```{r}
#2308
sum(data$LocationDescription =="ALLEY")
#用sum()取得案件發生地為胡同(data$LocationDescription為ALLEY)的觀察值數量
```


<br><br>

- - -

### Section-2 Understanding Dates in R

【2.1】 In what format are the entries in the variable Date?

+ Month/Day/Year Hour:Minute
+ Day/Month/Year Hour:Minute
+ Hour:Minute Month/Day/Year
+ Hour:Minute Day/Month/Year

```{r}
head(data$Date)
#透過觀看前六項Date,看出這個格式為Month/Day/Year Hour:Minute
```



```{r fig.height=2.5, fig.width=8}
#Month/Day/Year Hour:Minute
ts = as.POSIXct(data$Date, format="%m/%d/%y %H:%M") 
#本來是“字串”，將之轉換成時間資料格式，並命名為ts
head(ts)
```


【2.2】 What is the month and year of the median date in our dataset? 
```{r}
#2006年05月
format(median(ts), "%B")
format(median(ts), "%y")
#透過median()可了解中位數，再使用format將其轉為月份與年份
```


【2.3】 In which month did the fewest motor vehicle thefts occur?
```{r}
#2月
head(sort(table(format(ts,"%m"))),1)
#ts %>% format('%m') %>% table %>% sort %>% head(1)
#用format萃取月份參數，table總覽，並且使用sort排列，運用head(1)找出最少者
#可得為在2月，共發生13511起。
```

【2.4】 On which weekday did the most motor vehicle thefts occur?
```{r}
#週五
tail(sort(table(format(ts, "%w"))),1)
#ts %>% format('%w') %>% table %>% sort %>% tail(1)
#用format萃取星期參數，table總覽，並且使用sort排列，運用tail(1)找出最多者
#可得為在周五，共發生29284起
```

【2.5】 Which month has the largest number of motor vehicle thefts for which an arrest was made?
```{r}
#1月
tail(sort(table(format(ts[data$Arrest], "%m"))),1)
#ts[data$Arrest] %>% format('%m') %>% table %>% sort %>% tail(1)
#先找出有被逮捕的案件所屬時間，用format萃取月份參數，table總覽，並且使用sort排列，運用tail(1)找出最多者
#可得為一月,共1435起有被抓
```

<br><br>

- - -

### Section-3 Visualizing Crime Trends

【3.1】 (a) In general, does it look like crime increases or decreases from 2002 - 2012? (b) In general, does it look like crime increases or decreases from 2005 - 2008? (c) In general, does it look like crime increases or decreases from 2009 - 2011?
```{r}
# (a)2002~2012 : decrease
# (b)2005~2008 : decrease
# (c)2009~2011 : increase
hist(ts,"year",las=2,freq=T,xlab="")
#使用hist()直方圖來觀看年份之間的趨勢
```

【3.2】 Does it look like there were more crimes for which arrests were made in the first half of the time period or the second half of the time period?
```{r}
#上半年
median(ts[data$Arrest])
table(ts > as.POSIXct("2007-01-01"))
#被逮捕的案件發生時間中位數為2005.1.3,可得在上半年被逮捕的案件較多
```

【3.3】 For what proportion of motor vehicle thefts in 2001 was an arrest made?
```{r}
#0.10412
head(tapply(data$Arrest, format(ts,'%Y'), mean),1)
#使用tapply()看不同年份中,平均被逮捕數量的比例;並使用head(1),直接抓出2001年的資料
```

【3.4】 For what proportion of motor vehicle thefts in 2007 was an arrest made?
```{r}
#0.08487
prop_arrest=tapply(data$Arrest, format(ts,'%Y'), mean) 
prop_arrest[7]
#使用tapply()看不同年份中,平均被逮捕數量的比例,並將之設為prop_arrest
#再從prop_arrest中取出第七個(2007年)的資料
```

【3.5】 For what proportion of motor vehicle thefts in 2012 was an arrest made?
```{r}
#0.03903
prop_arrest=tapply(data$Arrest, format(ts,'%Y'), mean) 
prop_arrest[12]
#使用tapply()看不同年份中,平均被逮捕數量的比例,並將之設為prop_arrest
#再從prop_arrest中取出第12個(2012年)的資料
```

<br><br>

- - -

### Section-4 Popular Locations

【4.1】 Which locations are the top five locations for motor vehicle thefts, excluding the "Other" category? You should select 5 of the following options.

```{r}
#DRIVEWAY-RESIDENTIAL/GAS STATION/ ALLEY/ PARKING LOT GARAGE(NON.RESID.)/STREET 
table(data$LocationDescription) %>% sort %>% tail(6) %>% .[-4]
#用table總攬每個地點的發生次數,再用sort排序,最後使用tail找出top6,並將區域"other"忽略
#因此我們找出top5。
```

【4.2】 How many observations are in Top5?
```{r}
#177510
(D = names(table(data$LocationDescription) %>% sort %>% tail(6))[-4])
sum(data$LocationDescription %in% D)  # 177510

#我們運用4.1找出的top5,使用sum函數加總其觀察值數量
```

【4.3】 One of the locations has a much higher arrest rate than the other locations. Which is it? 
```{r}
#GAS STATION
Top5 = subset(data, LocationDescription %in% D)
tail(sort(tapply(Top5$Arrest, Top5$LocationDescription,mean)),1)
#使用tapply()看不同區域中,平均被逮捕數量的比例;並使用sort排序,接著運用tail(1),直接抓出最大比例的資料,即為AIRPORT VENDING ESTABLISHMENT
```

【4.4】 On which day of the week do the most motor vehicle thefts at gas stations happen?
```{r}
#禮拜六
which.max(table(format(ts[data$LocationDescription=="GAS STATION"], "%u")))
#將失竊地點設為加油站，用Format萃取星期參數，並總覽(table)星期一到日的失竊數，最後取出最多值(which.max)為周六
```

【4.5】 On which day of the week do the fewest motor vehicle thefts in residential driveways happen?
```{r}
#禮拜六
which.min(table(format(ts[data$LocationDescription=="DRIVEWAY - RESIDENTIAL"], "%u")))
#將失竊地點設為住宅車道，用Format萃取星期參數，並總覽(table)星期一到日的失竊數，最後取出最少值(which.min)為周六
```



<br><br><br>


