---
title: "AS3-3: 美國的人口統計和就業資料"
author: "第 15 組"
date: "`r Sys.time()`"
output: 
  html_document:
    highlight: pygments
    theme: flatly
    css: style.css
---

組員：`B044030015 許效軒`  `B046060036 王文弘`  `B054012011 黃冠綾`  `B046060027 姚詠馨`  `B046060035 張文瑜`  `M074020024 楊長舜`

```{r results='hide', message=FALSE, warning=FALSE, echo=FALSE}
# 這些程式碼設定網頁的格式，並安裝、載入一些基本的套件，請大家不要去改動<br>
rm(list=ls(all=T))
knitr::opts_chunk$set(comment = NA)
knitr::opts_knit$set(global.par = TRUE)
par(cex=0.8)
options(scipen=20, digits=4, width=90)
#
if(!require(pacman)) install.packages("pacman")
pacman::p_load(dplyr)
```
<hr>

就業統計數據是政策制定者用來衡量經濟整體實力的最重要指標之一。在美國，政府使用現有人口調查（CPS）衡量失業率，該調查每月收集來自各種美國人的人口統計和就業信息。在本練習中，我們將使用講座中審查的主題以及一些使用2013年9月版的，具有全國代表性的數據集。數據集中的觀察結果代表2013年9月CPS中實際完成調查的人員，完整數據集有385個欄位，但在本練習中，我們將使用數據集CPSData.csv版本，它具有以下欄位：

+ `PeopleInHousehold`: 受訪者家庭中的人數。
+ `Region`: 受訪者居住的人口普查區域。
+ `State`: 受訪者居住的州。
+ `MetroAreaCode`: 都會區代碼，如受訪者不住都會區，則為NA；從代碼到都會區名稱的對應在`MetroAreaCodes.csv`中提供。
+ `Age`: 受訪者的年齡，以年為單位。 80代表80-84歲的人，85代表85歲及以上的人。
+ `Married`: 受訪者的婚姻狀況。
+ `Sex`: 受訪者的性別。
+ `Education`: 受訪者獲得的最高教育程度。
+ `Race`: 受訪者的種族。
+ `Hispanic`: 受訪者是否屬於西班牙裔。
+ `CountryOfBirthcode`: 識別受訪者出生國家的代碼。從代碼到國家名稱的映射在CountryCodes.csv文件中提供。
+ `Citizenship`: 受訪者的公民身份。
+ `EmploymentStatus`: 受訪者的就業狀況。
+ `Industry`: 受訪者的就業行業（僅在受僱的情況下可用）。

- - -

<br><br>

###  Section-1 Loading and Summarizing the Dataset

__§ 1.1__ How many interviewees are in the dataset?
```{r}

CPS = read.csv("data/CPSData.csv")
nrow(CPS)#從列位數量可了解有多少個變數
#131302
```

__§ 1.2__ Among the interviewees with a value reported for the Industry variable, what is the most common industry of employment? Please enter the name exactly how you see it.
```{r}

summary(CPS$Industry)%>% sort#摘要Industry變數後再排序大小
#Educational and health services

```

__§ 1.3__ Which state has the fewest interviewees?
```{r}


summary(CPS$State)%>% sort%>%head(1)
#New Mexico
#摘要State變數後排序大小，再利用head尋找最小值
```

Which state has the largest number of interviewees?
```{r}
summary(CPS$State)%>% sort%>%tail(1)
#California
#摘要State變數後排序大小，再利用tail尋找最大值
```

__§ 1.4__ What proportion of interviewees are citizens of the United States?
```{r}

1-(sum(as.numeric(CPS$Citizenship=="Non-Citizen" , na.rm=TRUE))/ nrow(CPS))
#0.9421943
#令Citizenship=="Non-Citizen"為真者=1將其加總除上總資料筆數後，可得出Non-Citizen比例，將其使用1去減，則可得出Citizen的比例

```

__§ 1.5__ For which races are there at least 250 interviewees in the CPS dataset of Hispanic ethnicity? (Select all that apply.) 

+ American Indian
+ Asian
+ cBlack
+ Multiracial
+ Pacific Islander
+ White

```{r}

cps2=subset(CPS,CPS$Hispanic==1)
summary(cps2$Race)
#American Indian,cBlack, Multiracial,White
#篩選出Hispanic為1的資料後，針對其Race變數進行摘要
```

<br><br> 

- - -

###  Section-2 Evaluating Missing Values

__§ 2.1__ Which variables have at least one interviewee with a missing (NA) value? (Select all that apply.)

+ PeopleInHousehold
+ Region
+ State
+ MetroAreaCode
+ Age
+ Married
+ Sex
+ Education
+ Race
+ Hispanic
+ CountryOfBirthCode
+ Citizenship
+ EmploymentStatus
+ Industry

```{r}
colSums(is.na(CPS)) 

#MetroAreaCode,Married,Education,EmploymentStatus,Industry
#使用colSums()加總欄資料
```

__§ 2.2__  Which is the most accurate:

+ The Married variable being missing is related to the Region value for the interviewee.
+ The Married variable being missing is related to the Sex value for the interviewee.
+ The Married variable being missing is related to the Age value for the interviewee. 
+ The Married variable being missing is related to the Citizenship value for the interviewee.
+ The Married variable being missing is not related to the Region, Sex, Age, or Citizenship value for the interviewee.

```{r}
# The Married variable being missing is related to the Age value for the interviewee. 
table(CPS$Region, is.na(CPS$Married))
table(CPS$Sex, is.na(CPS$Married))
table(CPS$Age, is.na(CPS$Married))
table(CPS$Citizenship, is.na(CPS$Married))
#分別計算各變數與Married N/A值，發現在年齡變數中14歲以下皆為N/A值，故年齡變數與Married的missing data有關
```


__§ 2.3__ How many states had all interviewees living in a non-metropolitan area (aka they have a missing MetroAreaCode value)? For this question, treat the District of Columbia as a state (even though it is not technically a state).
```{r}
#Alaska,Wyoming,so answer is 2.  
table(CPS$State,is.na(CPS$MetroAreaCode))
#若MetroAreaCode在某國中全為N/A值，即False=0，則所有受訪者接居住在non-metropolitan area
```

How many states had all interviewees living in a metropolitan area? Again, treat the District of Columbia as a state.
```{r}
#District of Columbia,New Jersey,Rhode Island,so answer is 3.   
table(CPS$State,is.na(CPS$MetroAreaCode))
#若MetroAreaCode在某國中全無N/A值，即True=0，則所有受訪者接居住在metropolitan area
```

__§ 2.4__ Which region of the United States has the largest proportion of interviewees living in a non-metropolitan area?
```{r}
# Midwest,34.79%
table(CPS$Region, is.na(CPS$MetroAreaCode)) %>% prop.table(1)
#prop.table(x, margin=NULL)用來計算表格內百分比，當x=1時只計算列，x=2時只計算欄，預設的margin=NULL列與欄都會計算
#此處計算出Region與MetroAreaCode的表格後計算表格列的百分比得出Midwest比例為34.79%

```

__§ 2.5__ Which state has a proportion of interviewees living in a non-metropolitan area closest to 30%?
```{r}
# Wisconsin
table(CPS$State, is.na(CPS$MetroAreaCode)) %>% prop.table(1)
#prop.table(x, margin=NULL)用來計算表格內百分比，當x=1時只計算列，x=2時只計算欄，預設的margin=NULL列與欄都會計算
#此處計算出State與MetroAreaCode的表格後計算表格列的百分比得出Wisconsin比例為29.333%，最為接近30%
```

Which state has the largest proportion of non-metropolitan interviewees, ignoring states where all interviewees were non-metropolitan?
```{r}
# Montana, 83.6%
tapply(is.na(CPS$MetroAreaCode), CPS$State,mean)%>%sort()%>%tail()
#根據MetroAreaCode的錯誤值計算State的平均後，按照大小排列後取最大值
```

<br><br> 

- - -

###  Section-3 Integrating Metropolitan Area Data

__§ 3.1__ How many observations (codes for metropolitan areas) are there in MetroAreaMap?
```{r}
#271
Metro = read.csv("data/MetroAreaCodes.csv")
nrow(Metro)
#讀取csv.資料：read.csv("data/檔名.CSV")
```

How many observations (codes for countries) are there in CountryMap?
```{r}
#149
Country=read.csv("data/CountryCodes.csv")
nrow(Country)
```

__§ 3.2__ What is the name of the variable that was added to the data frame by the merge() operation?
```{r}
CPS_2= merge(CPS, Metro, by.x="MetroAreaCode", by.y="Code", all.x=TRUE)
# MetroArea
#當合併變數不同時merge()用法：merge(欲合併的data1,欲合併的data2, data1中變數名, data2中變數名,all.X=TRUE指若data2沒有與data1相同的值，則data2合併之變數為N/A)
```

How many interviewees have a missing value for the new metropolitan area variable?
```{r}
sum(is.na(CPS_2$MetroArea))
#34238
#is.na()可尋找missing data
```

__§ 3.3__ Which of the following metropolitan areas has the largest number of interviewees?
```{r}
table(CPS_2$MetroArea) %>% sort %>% tail(10)
#找最大的n筆data : tail(n)，若不輸入n值則為預設之5筆
#sort()可排序資料大小，由小至大排序
```

__§ 3.4__ Which metropolitan area has the highest proportion of interviewees of Hispanic ethnicity?
```{r}
#Laredo, TX ,0.9663
tapply(CPS_2$Hispanic, CPS_2$MetroArea, mean) %>% sort %>% tail
#根據metroarea計算Hispanic的平均後，按照大小排列後找出最大者
```

__§ 3.5__ Determine the number of metropolitan areas in the United States from which at least 20% of interviewees are Asian.
```{r}
#4
tapply(CPS_2$Race == "Asian", CPS_2$MetroArea, mean) %>% sort %>% tail
#根據metroarea計算Race的平均後，按照大小排列後找出最大者
```

__§ 3.6__  Passing na.rm=TRUE to the tapply function, determine which metropolitan area has the smallest proportion of interviewees who have received no high school diploma.
```{r}
#Iowa City, IA
tapply(CPS_2$Education == "No high school diploma", CPS_2$MetroArea, mean, na.rm=TRUE) %>% 
  sort %>% head
#找最小的n筆data :  head(n)，若不輸入n值則為預設之5筆
```


<br><br> 

- - -

###  Section-4 Integrating Country of Birth Data

__§ 4.1__ What is the name of the variable added to the CPS data frame by this merge operation?
```{r}
# Country
CPS_3= merge(CPS_2, Country, by.x="CountryOfBirthCode", by.y="Code", all.x=TRUE)
#當合併變數不同時merge()用法：merge(欲合併的data1,欲合併的data2, data1中變數名, data2中變數名,all.X=TRUE指若data2沒有與data1相同的值，則data2合併之變數為N/A)
```

How many interviewees have a missing value for the new metropolitan area variable?
```{r}
#176
sum(is.na(CPS_3$Country))
#is.na()的加總值為TRUE的個數
```

__§ 4.2__ Among all interviewees born outside of North America, which country was the most common place of birth?
```{r}
#Philippines,839x
table(CPS_3$Country) %>% sort %>% tail 
#將Country變數分類加總後排序，利用tail找出最大者
```

__§ 4.3__ What proportion of the interviewees from the "New York-Northern New Jersey-Long Island, NY-NJ-PA" metropolitan area have a country of birth that is not the United States? 
```{r}
# 0.3087
mean(CPS_3$Country[CPS_3$MetroArea=="New York-Northern New Jersey-Long Island, NY-NJ-PA"] 
     != "United States", na.rm=TRUE)
#由於"!="United States""本身為邏輯值，故直接球平均即可得出比例
```

__§ 4.4__ Which metropolitan area has the largest number (note -- not proportion) of interviewees with a country of birth in India? 
```{r}
# New York-Northern New Jersey-Long Island, NY-NJ-PA
tapply(CPS_3$Country == "India", CPS_3$MetroArea, sum, na.rm=TRUE) %>% 
  sort %>% tail(1)
#根據metroarea計算Country == "India"的加總後，按照大小排列後取最大值

```

In Brazil?
```{r}
# Boston-Cambridge-Quincy, MA-NH 
tapply(CPS_3$Country == "Brazil", CPS_3$MetroArea, sum, na.rm=TRUE) %>% sort %>% tail(1)
#根據metroarea計算Country == "Brazil"的加總後，按照大小排列後取最大值
```

In Somalia?
```{r}
# Minneapolis-St Paul-Bloomington, MN-WI
tapply(CPS_3$Country == "Somalia", CPS_3$MetroArea, sum, na.rm=TRUE) %>% sort%>% tail (1)
#根據metroarea計算Country == "Somalia"的加總後，按照大小排列後取最大值
```

<br><br><br>
