---
title: "AS3-2: 股市動態"
author: "第 15 組"
date: "`r Sys.time()`"
output:
  html_document:
    highlight: pygments
    theme: flatly
    css: style.css
---

組員：`B044030015 許效軒`  `B046060036 王文弘`  `B054012011 黃冠綾`  `B046060027 姚詠馨`  `B046060035 張文瑜`  `M074020024 楊長舜`

```{r results='hide', message=FALSE, warning=FALSE, echo=FALSE}
# 這些程式碼設定網頁的格式，並安裝、載入一些基本的套件，請大家不要去改動<br>
rm(list=ls(all=T))
knitr::opts_chunk$set(comment = NA)
knitr::opts_knit$set(global.par = TRUE)
par(cex=0.8)
options(scipen=20, digits=4, width=90)
#
if(!require(pacman)) install.packages("pacman")
pacman::p_load(dplyr)
```
<hr>

**股票動態**
fggggg
股票市場是買賣雙方交易公司股票的地方，也是個人和公司投資的最受歡迎的方式之一。現在估計世界股票市場規模達到數兆。紐約證券交易所位於紐約市，是世界上最大的股票市場。 紐約證券交易所約有2,800家上市公司。在這個問題上，我們將看看其中五家公司的每月股價：IB、通用電氣（GE）、寶潔、可口可樂和波音。此問題中使用的數據來自Infochimps。

使用`read.csv()`下載並讀取以下文件：

+ `data/IBMStock.csv`
+ `data/GEStock.csv`
+ `data/ProcterGambleStock.csv`
+ `data/CocaColaStock.csv`
+ `data/BoeingStock.csv` 

分別存入資料框`IBM`、`GE`、`ProcterGamble`、`CocaCola`和`Boeing`，
每個資料框都有兩個變量，描述如下：

+ `Date`：日期
+ `StockPrice`：給定月份公司的平均股價
```{r}
IBM = read.csv("data/IBMStock.csv")
GE = read.csv("data/GEStock.csv")
ProcterGamble = read.csv("data/ProcterGambleStock.csv")
CocaCola = read.csv("data/CocaColaStock.csv")
Boeing = read.csv("data/BoeingStock.csv")
```

在這個案例，我們將看看這些公司的股票動態如何隨著時間的推移而發生變化。

<br><hr>

###  Section-1 Summary Statistics

__§ 1.1__ Our five datasets all have the same number of observations. How many observations are there in each data set?
```{r}
nrow(IBM)
nrow(GE)
nrow(ProcterGamble)
nrow(CocaCola)
nrow(Boeing)

#480
```


__§ 1.2__ What is the earliest year in our datasets?
```{r}
head(IBM$Date,1) #head()可求出資料筆數最小之5筆，若要特定前n筆則為head(data,n)
head(GE$Date,1)
head(ProcterGamble$Date,1)
head(CocaCola$Date,1)
head(Boeing$Date,1)

#1/1/70
```

__§ 1.3__ What is the latest year in our datasets?
```{r}
tail(IBM$Date,1) #tail()可求出資料筆數最小之5筆，若要特定前n筆則為tail(data,n)
tail(GE$Date,1)
tail(ProcterGamble$Date,1)
tail(CocaCola$Date,1)
tail(Boeing$Date,1)

#12/1/09
```

__§ 1.4__ What is the mean stock price of IBM over this time period?
```{r}
mean(IBM$StockPrice)
#144.4
```

__§ 1.5__ What is the minimum stock price of General Electric (GE) over this time period?
```{r}
min(GE$StockPrice)
#9.294
```

__§ 1.6__ What is the maximum stock price of Coca-Cola over this time period?
```{r}
max(CocaCola$StockPrice)
#146.6
```

__§ 1.7__ What is the median stock price of Boeing over this time period?
```{r}
median(Boeing$StockPrice)
#44.88
```

__§ 1.8__ What is the standard deviation of the stock price of Procter & Gamble over this time period?
```{r}
sd(ProcterGamble$StockPrice)
#18.19
```

<br><hr>

###  Section-2 Visualizing Stock Dynamics

__§ 2.1__ Around what year did Coca-Cola has its highest stock price in this time period? Around what year did Coca-Cola has its lowest stock price in this time period?
```{r}
CocaCola$Date[which.max(CocaCola$StockPrice)]  
CocaCola$Date[which.min(CocaCola$StockPrice)]
#1/1/73 
#3/1/80

#比較：which.min可求出最小值位置；min()求出最小值
```


__§ 2.2__ In March of 2000, the technology bubble burst, and a stock market crash occurred. According to this plot, which company's stock dropped more?
```{r}
#Answer：GE(col="Green")

IBM$Date = as.Date(IBM$Date, "%m/%d/%y")

GE$Date = as.Date(GE$Date, "%m/%d/%y")

CocaCola$Date = as.Date(CocaCola$Date, "%m/%d/%y")

ProcterGamble$Date = as.Date(ProcterGamble$Date, "%m/%d/%y")

Boeing$Date = as.Date(Boeing$Date, "%m/%d/%y")

plot(CocaCola$Date[300:450], CocaCola$StockPrice[300:450], type="l",    
col="red",ylim=c(0,200),xlab = "Date",ylab="Stockprice")
lines(IBM$Date[300:450], IBM$StockPrice[300:450],col="brown")
lines(GE$Date[300:450], GE$StockPrice[300:450],col="Green")
lines(ProcterGamble$Date[300:450], ProcterGamble$StockPrice[300:450],col="pink")
lines(Boeing$Date[300:450], Boeing$StockPrice[300:450],col="Purple")
```

__§ 2.3__ (a) Around 1983, the stock for one of these companies (Coca-Cola or Procter and Gamble) was going up, while the other was going down. Which one was going up? 
```{r}
# ProcterGamble was going down
# Coca-Cola was going up
plot(CocaCola$Date[150:200], CocaCola$StockPrice[150:200], type="l",    
col="red",ylim=c(0,200),xlab = "Date",ylab="Stockprice")
lines(ProcterGamble$Date[150:200], ProcterGamble$StockPrice[150:200],col="pink")

```

(b) In the time period shown in the plot, which stock generally has lower values?
```{r}
#Answer：CocaCola 
```


<br><hr>

###  Section-3 Visualizing Stock Dynamics 1995-2005

__§ 3.1__ Which stock fell the most right after the technology bubble burst in March 2000?
```{r}
#Answer：GE

plot(CocaCola$Date[300:450], CocaCola$StockPrice[300:450], type="l",    
col="red",ylim=c(0,200),xlab = "Date",ylab="Stockprice")
lines(IBM$Date[300:450], IBM$StockPrice[300:450],col="brown")
lines(GE$Date[300:450], GE$StockPrice[300:450],col="Green")
lines(ProcterGamble$Date[300:450], ProcterGamble$StockPrice[300:450],col="pink")
lines(Boeing$Date[300:450], Boeing$StockPrice[300:450],col="Purple")

abline(v=as.Date(c("2000-01-01")), lwd=1)
abline(v=as.Date(c("1997-09-01")), lwd=1)
abline(v=as.Date(c("1997-11-01")), lwd=1)
abline(v=as.Date(c("2004-01-01")), lwd=1)
abline(v=as.Date(c("2006-01-01")), lwd=1)
```

__§ 3.2__ Which stock reaches the highest value in the time period 1995-2005?
```{r}
#Answer：IBM 
```

__§ 3.3__ In October of 1997, there was a global stock market crash that was caused by an economic crisis in Asia. Comparing September 1997 to November 1997, which companies saw a decreasing trend in their stock price? (Select all that apply.)
```{r}
#Answer：Procter and Gamble

#Answer：Boeing
```

__§ 3.4__ In the last two years of this time period (2004 and 2005) which stock seems to be performing the best, in terms of increasing stock price?
```{r}
#Answer：IBM
```


<br><hr>


###  Section-4 Monthly Trends

__§ 4.1__ For IBM, compare the monthly averages to the overall average stock price. In which months has IBM historically had a higher stock price (on average)? Select all that apply.
```{r}
#mean=144.4
#Answer：January,February,March,April,May
tapply(IBM$StockPrice,months(IBM$Date),mean)
summary(IBM$StockPrice)
```

__§ 4.2__ General Electric and Coca-Cola both have their highest average stock price in the same month. Which month is this?
```{r}
#GE
tapply(GE$StockPrice,months(GE$Date),mean)
#CocaCol
tapply(CocaCola$StockPrice,months(CocaCola$Date),mean)
#Answer：April
```

__§ 4.3__ For the months of December and January, every company's average stock is higher in one month and lower in the other. In which month are the stock prices lower?
```{r}
#GE

tapply(GE$StockPrice,months(GE$Date),mean)

#CocaCola

tapply(CocaCola$StockPrice,months(CocaCola$Date),mean)

#ProcterGamble

tapply(ProcterGamble$StockPrice,months(ProcterGamble$Date),mean)

#Boeing

tapply(Boeing$StockPrice,months(Boeing$Date),mean)

#IBM

tapply(IBM$StockPrice,months(IBM$Date),mean)

# Answer：January is lower
```

<br><br><br>

